\documentclass[11pt, oneside]{article}          % use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                           % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                                  % ... or a4paper or a5paper or ... 
\usepackage[parfill]{parskip}                  % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}                           % Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
\usepackage{multirow}

\title{Tending to a Garden}
\author{Kristoff A. Malejczuk}
\date{2023/3/4}

\begin{document}






























































Tending to a Garden

There is nobility in tending to a garden.
There is nobility in tending to a garden.
And I mean "tending to" in its fullest form.
% And I mean "garden" in its fullest form.
% There is nobility in tending to a garden.

What does it mean to tend to?
Tend comes from the Middle English "tenden", which is itself an abbreviation of "attenden".
Attenden means "to attend", and "to attend" means to pay attention.
So from an etymological perspective, "tending to" is referring to paying attention.
I don't love the word "pay", so I might instead say "giving attention" (because attention is a gift) or the "direction of attention".
So tending to is referring to the direction of attention.

Now, from a practical perspective, a dictionary perspective, "to tend to something" means "to care for something".
To tend to something, to really tend to it, is to care for, to cultivate, to nurture, to love.
Because how can you care for something without love?
Without love, "caring for" is just "looking after".

And I don't mean to care about, I mean to care for.
You can "care about" without love.
Caring about and caring for are very different things.
To "care about" means to be "invested in a particular outcome".
I can "care about" without love.
I care about keeping my shoes clean, I care about who wins the hockey game, I care about how much money I make, I care about making a good impression.
But "caring for" something is necessarily an act of love.
Caring for something is to love something.

So to tend to means "to care for", "to love", and it also means "to attend to", "to give attention".
To give attention lovingly.
Tending to is a loving attention.
Tending to is a nourishing application of love.
Tending to is love applied.
To tend to something, at its essence, in its highest form, is to give love.

There is nobility in tending to a garden.
And I mean tending to in its fullest form.
And I mean garden in its fullest form.
I haven't yet explored what a garden is.
We might actually be some type of garden.
But in the meantime, we at least know what it means to tend to.
To care for, to nourish, to cultivate, to love.
How beautiful.
So let's take a few moments to reflect on how we can tend to each other.
On how we can care for, nourish and love each other.
On how we can give loving attention.
Let's turn inwards and think about that for a few breaths.







%And we all know that where your attention goes, your energy flows.
%So tending to is a flow of loving energy.
%What a beautiful thing.
%What a gift.
%
%To tend to something is a state of loving attention.
%Loving attention, an energetic flowing of love.
%So in its highest form, "tending to something" is "giving love".
%
%
%
%
%To tend to 

















































\end{document}
